The code is organised into two Rust packages, $astro$ and $quantity$.

\section{Package \texorpdfstring{$astro$}{astro}}

$astro$ stands for ``Autonomous Swarm Tasking, Routing, and Organisation".
It is the main package. The Rust modules contained in this package are listed below.
\begin{itemize}
  \item $astro$. Defines struct $Astro$,
        which has member fields of type $Comm$, $Control$, $Gps$, and $Kinetics$.
        The software main loop mentioned in section \ref{sec:sft_arch} is implemented
        in this Rust module.
  \item $astroconf$. Contains configurations such as the radius of a UAV.
  \item $comm$. Defines struct $Comm$.
        This Rust module implements
        the functional module ``Communication" in section \ref{sec:sft_arch}.
  \item $control$. Defines struct $Control$,
        which has member fields of type $Contacts$, $NodeManager$, and $ColliVoid$.
        Implements the functional module ``Control" in section \ref{sec:sft_arch}.
        It has the following submodules.
    \begin{itemize}
      \item $collivoid$. Defines struct $ColliVoid$.
            Implements the functional module ``Collision Avoidance"
            in section \ref{sec:sft_arch}.
      \item $contacts$. Defines struct $Contacts$.
            Implements the functional module ``Contacts" in section \ref{sec:sft_arch}.
      \item $msg$. Defines struct $Msg$ and some other related types.
            Objects of $Msg$ type need to be transferred among UAVs as messages.
      \item $nm$. Defines struct $NodeManager$.
            Implements the functional module ``Node Management" in section \ref{sec:sft_arch}.
            Rust enum $NodeState$ is defined to represent the node states.
      \item $tm$. Defines struct $TaskManager$.
            Implements the functional module ``Task Management" in section \ref{sec:sft_arch}.
            It also defines structs $TaskDivider$ and $TaskExecutor$
            which are used to divide and execute a task.
    \end{itemize}
  \item $gps$. Defines struct $Gps$.
        Implements the functional module ``GPS" in section \ref{sec:sft_arch}.
  \item $kinetics$. Defines struct $Kinetics$.
        Implements the functional module ``Flight Kinetics" in section \ref{sec:sft_arch}.
        Some kinetic physical quantities are also defined here,
        e.g., $PosVec$ for position vector.
  \item $transceiver$. As there is no real hardware,
        $comm$, $gps$, and $kinetics$ actually interact with simulation infrastructure.
        The $transceiver$ module is an adapter
        between the three modules and the simulation infrastructure.
        It uses socket with non-blocking API as an inter-process communication method.
\end{itemize}

Serialisation and deserialisation are necessary for any software that
transfers internal data through network.
In package $astro$, Rust crate $serde$ is employed for this purpose.
$serde$ provides macro $Serialize$ and macro $Deserialize$,
which enable a type to serialise into and deserialise from a byte sequence.
All the structs defined in module $msg$ derive $Serialize$ and $Deserialize$,
since they need to be transferred as byte sequence through network.

The 32-bit unsigned integer type $u32$ is chosen as the type of UAV ID.
$Vec$<$u32$> is chosen as the type of NID.
Task ID is also of type $u32$.

\section{Package \texorpdfstring{$quantity$}{quantity}}

$quantity$ is an auxiliary package.
It defines $VectorF32$, which is a Rust macro.
After deriving $VectorF32$,
structs which are composed of $f32$ fields
can participate in some linear algebraic manipulations.
The struct $PosVec$ for position vector, and the struct $Velocity$ for velocity vector,
which are both 3D kinematic quantities defined in $kinetics$ module,
derive this macro.